\documentclass[../../../main.tex]{subfiles}

% break line on the "Separability theorem".

\begin{document}
\begin{multicols}{2}[\section{Galois theory}]
  \subsection{Introduction}
  \subsubsection{Rings, integral domains and fields}
  \begin{prop}
    \hfill
    \begin{enumerate}
      \item A subring of an integral domain is an integral domain.
      \item A field is an integral domain.
      \item A subring of a field is an integral domain.
    \end{enumerate}
  \end{prop}
  \begin{lemma}
    Let $K$ be a field and $R\ne\{0\}$ be a ring. Then, all ring morphisms $f:K\rightarrow R$ are injective.
  \end{lemma}
  \begin{definition}
    Let $K$, $L$ be fields. A \textit{field morphism between $K$ and $L$} is a ring morphism $K\rightarrow L$.
  \end{definition}
  \begin{lemma}
    Let $R$ be a ring. Then, there exists a unique ring morphism $f:\ZZ\rightarrow R$ satisfying:
    \begin{itemize}
      \item $f(1+\overset{(n)}{\cdots}+1)=1_R+\overset{(n)}{\cdots}+1_R$ if $n\geq 1$.
      \item $f(n)=-f(-n)$ if $n\leq -1$.
    \end{itemize}
  \end{lemma}
  \begin{definition}
    Let $R$ be a ring and $f:\ZZ\rightarrow R$ be the ring morphism from $\ZZ$ to $R$. The \textit{characteristic of $R$}, $\ch (R)$, is defined to be the value of $n$ such that $\ker f=\quot{\ZZ}{n\ZZ}$.
  \end{definition}
  \begin{prop}
    Let $K$ be a field. Then, either $\ch(K)$ is prime or $\ch(K)=0$.
  \end{prop}
  \begin{definition}
    Let $R$ be a ring. We define the  \textit{polynomial ring $R[x]$} as: $$R[x]:=\{r_0+r_1\cdot x+\cdots+r_n\cdot x^n:r_i\in R\ \forall i\text{ and }n\geq 0\}$$ Moreover, we can iterate this definition to define the polynomial ring in $m$-unknowns: $$R[x_1,\ldots,x_m]=\left(R[x_1,\ldots,x_{m-1}]\right)[x_m]$$
  \end{definition}
  \begin{prop}[Universal property of polynomials in several variables]
    Let $R$, $S$ be two rings, $f:R\rightarrow S$ be a ring morphism and $s_1,\ldots,s_n\in S$ be not necessarily distinct elements of $S$. Then, the function $\varphi:R[x_1,\ldots,x_n]\rightarrow S$ defined by
    \begin{multline*}
      \varphi\left(\sum_{i_1,\ldots,i_n\geq 0}r_{i_1,\ldots,i_n}{x_1}^{i_1}\cdots {x_n}^{i_n}\right)=\\=\sum_{i_1,\ldots,i_n\geq 0}f(r_{i_1,\ldots,i_n}){s_1}^{i_1}\cdots {s_n}^{i_n}
    \end{multline*}
    is the unique ring morphism such that $\varphi(r)=f(r)$ $\forall r\in R$ and $\varphi(x_i)=s_i$ for $i=1,\ldots,n$. This function is called \textit{evaluation of $s_1,\ldots,s_n$ through $f$}\footnote{For the case $n=1$, we will denote by $\varphi_s$ the unique ring morphism $\varphi_s:R[x]\rightarrow S$ such that $\varphi_s(r)=f(r)$ $\forall r\in R$ and $\varphi_s(x)=s$.}.
  \end{prop}
  \subsubsection{Field of fractions}
  \begin{theorem}[Universal property of the field of fractions]
    All integral domains are a subring of a field. More explicitly, if $R$ is an integral domain and $K$ is a field, there exists another field $Q(R)$ and an injective ring morphism $\iota:R\hookrightarrow Q(R)$ so that for all injective ring morphism $f:R\hookrightarrow K$, there exists a unique field morphism $\psi_f:Q(R)\rightarrow K$ defined by
    $$
      \function{\psi_f}{Q(R)}{K}{\displaystyle\frac{a}{b}}{f(a){f(b)}^{-1}}
    $$
    such that $f=\psi_f\circ\iota$.
  \end{theorem}
  \begin{corollary}
    Let $R$ be an integral domain. The field $Q(R)$ with the injection $\iota$ is unique up to isomorphism, that is, if there is a field $Q'(R)$ and an injective ring morphism $\iota':R\hookrightarrow Q'(R)$ satisfying the property of above, then there is a unique isomorphism $\psi_{\iota'}:Q(R)\cong Q'(R)$ such that $\iota'=\psi_{\iota'}\circ\iota$, where $\iota:R\hookrightarrow Q(R)$. This field $Q(R)$ is called \textit{field of fractions of $R$}.
  \end{corollary}
  \begin{definition}
    Let $K$ be a field. The field of fractions of $K[x]$ is defined as $K(x):=Q(K[x])$ and it is called \textit{field of rational functions}. More generally, the field of fractions of $K[x_1,\ldots,x_n]$ is defined as: $$K(x_1,\ldots,x_n):=Q(K[x_1,\ldots,x_n])$$
  \end{definition}
  \begin{lemma}
    Let $R$ be an integral domain. Then, $R[x]$ is also an integral domain and: $$Q(R[x])\cong Q(R)(x)$$
  \end{lemma}
  \begin{corollary}
    Let $K$ be a field. For all $n\geq 2$ we have: $$K(x_1,\ldots,x_n)\cong K(x_1,\ldots,x_{n-1})(x_n)$$
  \end{corollary}
  \subsubsection{Subring and subfield generated by a set}
  \begin{definition}
    Let $(R,+,\cdot)$ be a ring and $X\subseteq R$ be a subset of $R$. Let $$P:=\{S\subseteq R: X\subseteq S,(S,+,\cdot)\text{ is a subring of }(R,+,\cdot)\}$$ Then, the smallest subring of $(R,+,\cdot)$ containing $X$ is: $$\langle X\rangle_\text{ring}=\bigcap_{S\in P}S$$
  \end{definition}
  \begin{definition}
    Let $R$ be a ring, $S\subseteq R$ be a subring of $R$ and $A\subseteq R$ be a subset of $R$. Then, the smallest subring of $R$ containing $S$ and $A$ is denoted by $S[A]$.
  \end{definition}
  \begin{lemma}
    Let $A$ be a finite set, $R$ and $S$ be rings and $\varphi:R[x_a:a\in A]\rightarrow S$ be the evaluation morphism such that $\varphi(r)=r$ $\forall r\in R$ and $\varphi(x_a)=a$ $\forall a\in A$. Then, $S[A]=\im\varphi$.
  \end{lemma}
  \begin{definition}
    Let $(K,+,\cdot)$ be a field and $X\subseteq K$ be a subset of $K$. Let $$P:=\{L\subseteq K: X\subseteq L,(L,+,\cdot)\text{ is a subfield of }(R,+,\cdot)\}$$ Then, the smallest subfield of $(K,+,\cdot)$ containing $X$ is: $$\langle X\rangle_\text{field}=\bigcap_{L\in P}L$$
  \end{definition}
  \begin{definition}
    Let $L$ be a field, $K\subseteq L$ be a subfield of $L$ and $A\subseteq L$ be a subset of $L$. Then, the smallest subfield of $L$ containing $K$ and $A$ is denoted by $K(A)$.
  \end{definition}
  \subsection{Field extensions}
  \begin{prop}
    Let $K$, $L$ be fields. Then, any field morphism $K\rightarrow L$ is injective.
  \end{prop}
  \begin{definition}
    Let $K$, $L$ be two fields. A \textit{field extension $\quot{L}{K}$} is a field morphism $K\hookrightarrow L$.
  \end{definition}
  \begin{prop}
    Let $\quot{L}{K}$ be a field extension. Then, $L$ is a vector space over $K$. Reciprocally, if $L$ is a vector space over $K$ satisfying: $$(\lambda\cdot 1)\cdot(\mu\cdot 1)=(\lambda\cdot\mu)\cdot 1\qquad\forall\lambda,\mu\in K$$ then the morphism $f:K\rightarrow L$ defined as $f(\lambda)=\lambda\cdot 1$ is a field morphism and $\quot{L}{K}$ is a field extension.
  \end{prop}
  \begin{definition}
    Let $\quot{L}{K}$ be a field extension. We define the \textit{degree of the extension $\quot{L}{K}$} as: $$[L:K]:=\dim_K(L)$$ We say that the extension $\quot{L}{K}$ is \textit{finite} if $[L:K]$ is finite. Otherwise, we say that $\quot{L}{K}$ is \textit{infinite}.
  \end{definition}
  \begin{lemma}[Kronecker lemma]
    Let $K$ be a field, $p(x)\in K[x]$ a monic and irreducible polynomial of degree $d\geq 1$ and $L=\quot{K[x]}{(p(x))}$. Then, $\quot{L}{K}$ is a field extension of degree $d$, and the set $\{1,\bar{x},\ldots,{\bar{x}}^{d-1}\}$ is a basis of the vector space $L$ over $K$. Furthermore, $\bar{x}\in L$ is a root of $p(x)$ in $L$.
  \end{lemma}
  \subsubsection{Algebraic and transcendental numbers}
  \begin{definition}
    Let $\quot{L}{K}$ be a field extension and $\alpha\in L$. Consider the ring morphism: $$\function{\varphi_\alpha}{K[x]}{L}{p(x)}{p(\alpha)}$$
    \begin{enumerate}
      \item We say that $\alpha$ is \textit{algebraic over $K$} if $\ker\varphi_\alpha=(p(x))$, where $p(x)\in K[x]$ is irreducible polynomial of degree $d\geq 1$. This polynomial is called \textit{irreducible polynomial of $\alpha$ over $K$} and it is denoted by $\irr(\alpha,K)(x)$.
      \item We say that $\alpha$ is \textit{transcendental over $K$} if $\ker\varphi_\alpha=(0)$, or equivalently, if it is not algebraic.
    \end{enumerate}
  \end{definition}
  \begin{theorem}
    Let $\overline{\QQ}\subset\CC$ be the set of algebraic numbers in $\QQ$. Then, $\overline{\QQ}$ is countable.
  \end{theorem}
  \subsubsection{Simple extensions}
  \begin{definition}
    A field extension $\quot{L}{K}$ is called \textit{simple} if $L=K(\alpha)$ for some $\alpha\in L$.
  \end{definition}
  \begin{prop}
    Let $\quot{L}{K}$ be a field extension and $\alpha\in L$. Then:
    \begin{itemize}
      \item If $\alpha$ is algebraic over $K$, then: $$K(\alpha)=K[\alpha]\cong\quot{K[x]}{(\irr(\alpha,K)(x))}$$
      \item If $\alpha$ is transcendental over $K$, then: $$K(\alpha)\cong K(x)$$
    \end{itemize}
  \end{prop}
  \begin{corollary}
    Let $\quot{L}{K}$ be a field extension and $\alpha\in L$. Then, $\quot{K(\alpha)}{K}$ is finite if and only if $\alpha$ is algebraic over $K$. Furthermore in that case: $$[K(\alpha):K]=\deg(\irr(\alpha,K)(x))$$
  \end{corollary}
  \begin{theorem}[Tower formula]
    Let $\quot{F}{L}$ and $\quot{L}{K}$ be field extensions. Then: $$[F:K]=[F:L][L:K]$$
  \end{theorem}
  \begin{prop}
    Let $\quot{L}{K}$ be a field extension and $\alpha\in L$ be algebraic. Then:
    \begin{enumerate}
      \item The following statements are equivalent:
            \begin{enumerate}
              \item $\alpha\in K$
              \item $\irr(\alpha,K)(x)=x-\alpha$
              \item $\deg(\irr(\alpha,K)(x))=1$
            \end{enumerate}
      \item If $\quot{K'}{K}$ is another field extension, then: $$\irr(\alpha,K')(x)\mid\irr(\alpha,K)(x)$$ and, moreover, $\irr(\alpha,K')(x)=\irr(\alpha,K)(x)\iff\deg(\irr(\alpha,K')(x))=\deg(\irr(\alpha,K)(x))$.
      \item $\deg(\irr(\alpha,K)(x))\mid [L:K]$
    \end{enumerate}
  \end{prop}
  \begin{definition}
    Let $n\in\NN$ and $K_0,\ldots,K_n$ be fields. A \textit{tower of fields} is a sequence of field extensions $\quot{K_j}{K_{j-1}}$ for $j=1,\ldots,n$. We will denoted this tower of fields as: $$K_n/K_{n-1}/\cdots/K_0$$
  \end{definition}
  \begin{corollary}
    Let $n\in\NN$ and $$K_n/K_{n-1}/\cdots/K_0$$ be a tower of fields. Then: $$[K_n:K_0]=[K_n:K_{n-1}][K_{n-1}:K_{n-2}]\cdots[K_1:K_0]$$
  \end{corollary}
  \begin{definition}
    A field extension $\quot{L}{K}$ is called \textit{finitely generated} if there exists $\alpha_1,\ldots,\alpha_n\in L$ such that $L=K(\alpha_1,\ldots,\alpha_n)$.
  \end{definition}
  \subsubsection{Algebraic extensions}
  \begin{definition}
    Let $\quot{L}{K}$ be a field extension. We say that $\quot{L}{K}$ is \textit{algebraic} if $\forall\alpha\in L$, $\alpha$ is algebraic over $K$.
  \end{definition}
  \begin{definition}
    Let $\quot{L}{K}$ be a field extension. We say that $\quot{L}{K}$ is \textit{purely transcendental} if $\forall\alpha\in L\setminus K$, $\alpha$ is transcendental over $K$.
  \end{definition}
  \begin{lemma}
    Let $\quot{L}{K}$ be a finite field extension. Then, $\quot{L}{K}$ is algebraic.
  \end{lemma}
  \begin{prop}
    Let $\quot{L}{K}$ be a field extension. The following are equivalent:
    \begin{enumerate}
      \item $\quot{L}{K}$ is finite.
      \item $\quot{L}{K}$ is algebraic and there exist $\alpha_1,\ldots,\alpha_n\in L$ such that $L=K(\alpha_1,\ldots,\alpha_n)$.
      \item There exist $\alpha_1,\ldots,\alpha_n\in L$ with $\alpha_i$ algebraic over $K(\alpha_1,\ldots,\alpha_{i-1})$ for $i=1,\ldots,n$ such that $L=K(\alpha_1,\ldots,\alpha_n)$.
    \end{enumerate}
  \end{prop}
  \begin{prop}
    Let $F/L/K$ be a tower of fields such that $\quot{L}{K}$ is algebraic, and $\alpha\in F$. Then, if $\alpha$ is algebraic over $L$, $\alpha$ is algebraic over $K$.
  \end{prop}
  \begin{prop}
    Let $F/L/K$ be a tower of fields. Then:
    \begin{enumerate}
      \item If $\quot{L}{K}$ is algebraic, any subring $R$ such that $K\subseteq R\subseteq L$ is a subfield.
      \item $\quot{L}{K}$ and $\quot{F}{L}$ are algebraic $\iff\quot{F}{K}$ is algebraic.
      \item If $\alpha,\beta\in L$ are algebraic over $K$, then so are $\alpha+\beta$, $\alpha\beta$ and $\alpha\beta^{-1}$ (if $\beta\ne 0$).
      \item The set $$E:=\{\alpha\in L:\alpha\text{ is algebraic over }K\}$$ is a subfield of $L$, the field extension $\quot{E}{K}$ is algebraic and if $L\ne E$, then $\quot{L}{E}$ is purely transcendental.
    \end{enumerate}
  \end{prop}
  \subsubsection{Morphisms of extensions}
  \begin{definition}
    Let $K$, $L$, $F$ be fields and $f:K\hookrightarrow L$ and $g:K\hookrightarrow F$ be field extensions. A \textit{morphism of field extensions between $f$ and $g$} (sometimes called $K$-field morphism) is a field morphism $h:L\rightarrow F$ such that $h|_K=g$, where $h|_K:=h\circ f$\footnote{If the morphisms $f$ and $g$ are the natural inclusions, we will denote $h|_K:=\id_K$.}. The set of all such morphisms is:
    $$\Mor_K(f,g):=\{h:L\longrightarrow F:h\circ f=g\}$$
    If $f$ and $g$ are the natural inclusions, we will denote: $$\Mor_K(L,F):=\Mor_K(f,g)=\{h:L\longrightarrow F:h|_K=\id_K\}$$
    If $f$ is the natural inclusion but $g$ isn't, we will denote: $$\Mor_K(L,g):=\Mor_K(f,g)=\{h:L\longrightarrow F:h|_K=g\}$$
    Finally, if $g$ is the natural inclusion but $f$ isn't, we will denote: $$\Mor_K(f,F):=\Mor_K(f,g)=\{h:L\longrightarrow F:h\circ f=\id_K\}$$
  \end{definition}
  \begin{definition}
    Let $K$, $L$, $F$ be fields and $f:K\hookrightarrow L$ and $g:K\hookrightarrow F$ be field extensions. We define the following sets:
    \begin{gather*}
      \Iso_K(f,g):=\{h\in\Mor_K(f,g):h\text{ is bijective}\} \\
      \Aut_K(f):=\Iso_K(f,f)
    \end{gather*}
    If $f$ and $g$ are the natural inclusions, we will denote\footnote{And we define $\Iso_K(L,g)$ and $\Iso_K(f,F)$ analogously as we did before.}:
    \begin{gather*}
      \Iso_K(L,F):=\{h\in\Mor_K(L,F):h\text{ is bijective}\} \\
      \Aut_K(L):=\Iso_K(L,L)
    \end{gather*}
  \end{definition}
  \begin{lemma}
    Let $\quot{L}{K}$ be a field extension. Then, $(\Aut_K(L),\circ)$ is a group and it is called \textit{Galois group of $\quot{L}{K}$}. Hence, $\Aut_K(L)$ is also denoted as $\Gal(\quot{L}{K})$\footnote{For the general case when $f:K\hookrightarrow L$ is a field extension, we define $\Gal(f):=\Aut_K(f)$.}.
  \end{lemma}
  \begin{lemma}
    Let $K$, $L$, $F$ be fields and $f:K\rightarrow L$, $g:K \rightarrow F$ be field morphisms. Let $h\in\Mor_K(f,g)$, $\alpha\in L$, and $p(x)\in K[x]$. Then: $$h(f(p)(\alpha))=g(p)(h(\alpha))$$
    If $f$ and $g$ are the natural inclusions, then: $$h(p(\alpha))=p(h(\alpha))$$
  \end{lemma}
  \begin{lemma}
    Let $\quot{L}{K}$, $g:K \hookrightarrow F$ be field extensions and $\alpha\in L$ be algebraic over $K$. Then, we have the following bijection: $$\Mor_K(K(\alpha),g)\cong\{\beta\in F:g(\irr(\alpha,K))(\beta)=0\}$$
    If $g$ is the natural inclusion, then: $$\Mor_K(K(\alpha),F)\cong\{\beta\in F:\irr(\alpha,K)(\beta)=0\}$$
  \end{lemma}
  \begin{corollary}
    Let $\quot{K(\alpha)}{K}$ be a finite field extension. Then, $\Gal(\quot{K(\alpha)}{K})$ is finite and:
    $$\textstyle|\Gal(\quot{K(\alpha)}{K})|=|\{\beta\in K(\alpha):\irr(\alpha,K)(\beta)=0\}|$$
    and therefore: $$\textstyle|\Gal(\quot{K(\alpha)}{K})|\leq[K(\alpha):K]$$
  \end{corollary}
  \begin{prop}
    Let $K$, $L$, $F$ be fields and $f:K\hookrightarrow L$ and $g:K\hookrightarrow F$ be field extensions. Then:
    \begin{enumerate}
      \item If $f':K\rightarrow L'$, $\varphi:L'\rightarrow L$ are field extensions, then: $$\Mor_K(f,g)=\bigsqcup_{h\in\Mor_K(f',g)}\Mor_{L'}(\varphi,h)$$
            In particular, if $f$, $g$, $f'$ and $\varphi$ are the natural inclusions, then:
            $$\Mor_K(L,F)=\bigsqcup_{h\in\Mor_K(L',F)}\Mor_{L'}(L,h)$$
      \item If $\Iso_K(f,g)\ne\varnothing$, then $\Iso_K(f,g)\cong\Gal(f)$ by sending $h\mapsto h\circ {h_0}^{-1}$, where $h_0\in\Iso_K(f,g)$ is a fixed isomorphism.

            Analogously, if $\Iso_K(L,F)\ne\varnothing$, then $\Iso_K(L,F)\cong\Gal(\quot{L}{K})$.
    \end{enumerate}
  \end{prop}
  \subsection{Finite fields}
  \begin{definition}
    A \textit{finite field} $F$ is a finite set which is a field.
  \end{definition}
  \begin{prop}
    Let $F$ be a finite field. Then, $F=p^n$ where $p$ is a prime number and $n\in\NN$.
  \end{prop}
  \begin{theorem}
    Let $p$ be a prime number and $n\in\NN$. Then, there exists a unique field with $p^n$ elements up to isomorphism which will be denoted as $\FF_{p^n}$\footnote{Another commonly used notation to denote the field with $p^n$ elements is $\text{GF}(p^n)$.}.
  \end{theorem}
  \begin{prop}
    Let $p$ be a prime number and $d,n\in\NN$. Then: $$\FF_{p^d}\subseteq\FF_{p^n}\iff d\mid n$$
  \end{prop}
  \begin{theorem}
    Let $p$ be a prime number and $d\in\NN$. We define the set $P_d$ as:
    \begin{multline*}
      P_{p,d}:=\{f(x)\in\FF_p[x]:\deg(f(x))=d\text{ and}\\\text{$f(x)$ is monic and irreducible}\}
    \end{multline*}
    Then, for all $n\in\NN$ we have: $$x^{p^n}-x=\prod_{d\mid n}\prod_{f(x)\in P_{p,d}}f(x)$$
  \end{theorem}
  \begin{corollary}
    Let $p$ be a prime number and $d,n\in\NN$. Then: $$p^n=\sum_{d\mid n}d|P_{p,d}|$$
  \end{corollary}
  \begin{corollary}
    For all prime number $p$ and for all $n\in\NN$, there exists a monic and irreducible polynomial of degree $n$ in $\FF_p[x]$.
  \end{corollary}
  \begin{corollary}
    Let $p$ be a prime number and $n\in\NN$. Then, $\FF_{p^n}=\FF_p(\alpha)$ for some $\alpha\in\FF_{p^n}$. Thus, the extension $\quot{\FF_{p^n}}{\FF_p}$ is simple.
  \end{corollary}
  \begin{definition}
    Let $p$ be a prime number $R$ be a ring such that $\ch R=p$. We define the \textit{Frobenius endomorphism} as: $$\function{\text{Frob}_R}{R}{R}{r}{r^p}$$
  \end{definition}
  \begin{theorem}
    Let $p$ be a prime number and $n\in\NN$. Then, $\text{Frob}_{\FF_{p^n}}\in\Gal(\quot{\FF_{p^n}}{\FF_p})$ and, furthermore: $$\Gal(\FF_{p^n}/\FF_p)=\langle\text{Frob}_{\FF_{p^n}}\rangle\cong\quot{\ZZ}{n\ZZ}$$
  \end{theorem}
  \begin{corollary}
    Let $p$ be a prime number, $n\in\NN$, $q=p^n$ and denote $\text{Frob}_q:={\left(\text{Frob}_{\FF_{p^n}}\right)}^n$. Then, for all $r\in\NN$: $$\Gal(\FF_{q^r}/\FF_q)=\langle\text{Frob}_q\rangle\cong\quot{\ZZ}{r\ZZ}$$
  \end{corollary}
  \begin{definition}[Perfect fields]
    A field $K$ is called \textit{perfect} if either $\ch K=0$ or $\ch K=p>0$ and $\text{Frob}_K\in\Aut(K)$.
  \end{definition}
  \subsection{Algebraic field extensions}
  \subsubsection{Splitting field}
  \begin{definition}
    Let $K$ be a field and $p(x)\in K[x]$ be a polynomial such that $\deg p(x)=n\geq 1$. We say that $p(x)$ \textit{splits into linear factors} on $K$ if $p(x)=a_n\prod_{i=1}^n(x-a_i)$, where $a_i\in K$ for $i=1,\ldots,n$.
  \end{definition}
  \begin{theorem}[Kronecker theorem]
    Let $K$ be a field and $S\subset K[x]$ be a finite set. Then, there exists a finite field extension $\quot{L}{K}$ such that all polynomials in $S$ split into linear factors on $L$.
  \end{theorem}
  \begin{theorem}
    Let $K$ be a field, $L=K(\alpha_1,\ldots,\alpha_n)$ and consider a finite field extension $\quot{L}{K}$. Let $f:K\hookrightarrow F$ be a field morphism such that $f(\irr(\alpha_i,K)(x))$ splits into linear factors on $F$ for all $i=1,\ldots,n$. Then, $$1\leq|\Mor_K(L,f)|\leq [L:K]$$ and, furthermore, $|\Mor_K(L,f)|=[L:K]$ if and only if $f(\irr(\alpha_i,K)(x))$ has no repeated roots on $F$ for all $i=1,\ldots,n$.
  \end{theorem}
  \begin{definition}[Splitting field]
    Let $\quot{L}{K}$ be a finite field extension and $p(x)\in K[x]\setminus K$ be such that it splits into linear factors in $L$. Let $\alpha_1,\ldots,\alpha_n$ be their roots. The \textit{splitting field of $p(x)$ over $K$} is the least subfield $K(\alpha_1,\ldots,\alpha_n)$ of $L$ where $p(x)$ splits into linear factors.
  \end{definition}
  \begin{prop}
    Let $K$ be a field and $p(x)\in K[x]\setminus K$. Then, $L$ is a splitting field of $p(x)$ if and only if:
    \begin{enumerate}
      \item $p(x)$ splits into linear factors on $L$.
      \item For all $L/F/K$ tower of fields with $F\ne L$, $p(x)$ doesn't split into linear factors on $F$.
    \end{enumerate}
  \end{prop}
  \begin{theorem}[Existence of the splitting field]
    Let $K$ be a field and $p(x)\in K[x]\setminus K$. Then, there exists a splitting field of $p(x)$ over $K$.
  \end{theorem}
  \begin{theorem}
    Let $K$ be a field, $p(x)\in K[x]\setminus K$ and $\quot{L}{K}$ and $\quot{F}{K}$ be two splitting fields of $p(x)$ over $K$. Then, $[L:K]=[F:K]$ and $$1\leq|\Iso_K(L,F)|\leq [L:K]$$ Furthermore, $|\Iso_K(L,F)|=[L:K]$ if and only if all irreducible factors of $p(x)$ have no repeated roots on $F$.
  \end{theorem}
  \begin{corollary}[Unicity of the splitting field]
    Let $K$ be a field and $p(x)\in K[x]\setminus K$. Then, any two splitting fields of $p(x)$ over $K$ are isomorphic.
  \end{corollary}
  \begin{corollary}
    Let $K$ be a field, $p(x)\in K[x]\setminus K$ and $L$ be the splitting field of $p(x)$ over $K$. Then: $$\textstyle\left|\Gal\left(\quot{L}{K}\right)\right|\leq[L:K]$$ and if $p(x)$ has no repeated roots on $L$, then: $$\textstyle\left|\Gal\left(\quot{L}{K}\right)\right|=[L:K]$$
  \end{corollary}
  \begin{corollary}
    Let $\quot{F}{K}$ be a field extension and $p(x)\in K[x]$. Then, the splitting field $L_F$ of $p(x)$ over $F$ contains the splitting field $L$ of $p(x)$ over $K$
  \end{corollary}
  \subsubsection{Normal extensions}
  \begin{definition}
    An algebraic field extension $\quot{L}{K}$ is \textit{normal} if $\forall p(x)\in K[x]$, irreducible over $K$, then: if $p(x)$ has a root in $L$, then $p(x)$ splits into linear factors in $L$.
  \end{definition}
  \begin{theorem}
    Let $\quot{L}{K}$ be finite field extension. $\quot{L}{K}$ is normal if and only if it is the splitting field of some polynomial $p(x)\in K[x]\setminus K$.
  \end{theorem}
  \begin{corollary}
    Let $\quot{L}{K}$ be finite field extension. Then, there exists a field extension $\quot{F}{L}$ such that:
    \begin{enumerate}
      \item $\quot{F}{K}$ is finite and normal.
      \item For all field extensions $\quot{H}{L}$ with $\quot{H}{K}$ normal there is at least one $L$-field morphism $f:F\rightarrow H$.
    \end{enumerate}
    The extension $\quot{F}{L}$ is called \textit{normal closure of $\quot{L}{K}$}.
  \end{corollary}
  \begin{corollary}
    Let $L/F/K$ be a tower of fields such that $\quot{L}{K}$ is finite and normal. Then, $\quot{L}{F}$ is also finite and normal.
  \end{corollary}
  \begin{corollary}
    Let $L/F/K$ be a tower of fields such that $\quot{L}{K}$ is finite and normal. Let $f\in\Mor_K(F,L)$. Then, there exists at least one automorphism $\varphi\in\Gal(\quot{L}{K})$ such that $\varphi|_F=f$.
  \end{corollary}
  \begin{corollary}
    Let $\quot{L}{K}$ be a finite field extension. Then: $$\textstyle|\Gal(\quot{L}{K})|\leq[L:K]$$ Hence, $\Gal(\quot{L}{K})$ is a finite group.
  \end{corollary}
  \begin{corollary}
    Let $L/F/K$ be a tower of fields such that $\quot{L}{K}$ is finite and normal. Then, $\quot{F}{K}$ is normal if and only if $\varphi(F)=F$ $\forall\varphi\in\Gal(\quot{L}{K})$.
  \end{corollary}
  \subsubsection{Separable polynomials}
  \begin{definition}[Formal derivative]
    Let $R$ be a ring and $p(x)=\sum_{n=0}^da_nx^n\in R[x]$. We define \textit{formal derivative of $p(x)$} as: $$p'(x):=\sum_{n=1}^dna_nx^{n-1}$$
  \end{definition}
  \begin{prop}
    Let $R$ be a ring, $a\in R$ and $p(x),q(x)\in R[x]$. Then:
    \begin{enumerate}
      \item ${(p(x)+q(x))}'=p'(x)+q'(x)$
      \item $(ap(x))'=ap'(x)$
      \item $(p(x)q(x))'=p'(x)q(x)+p(x)q'(x)$
      \item If $\ch(R)=0$ or $\gcd(\ch(R),\deg(p(x)))=1$, then: $$\deg(p'(x))\leq\deg(p(x))-1$$
    \end{enumerate}
  \end{prop}
  \begin{prop}
    Let $K$ be a field, $p(x)\in K[x]\setminus K$, $L$ be a splitting field of $p(x)$ over $K$ and $d(x):=\gcd(p(x),p'(x))$. Then:
    $$\{\alpha\in L:d(\alpha)=0\}=\{\alpha\in L:{(x-\alpha)}^2\mid p(x)\}$$
  \end{prop}
  \begin{definition}
    Let $K$ be a field and $p(x)\in K[x]$. We say that $p(x)$ is \textit{separable} if it doesn't have multiple roots in its splitting field.
  \end{definition}
  \begin{corollary}
    Let $K$ be a field, $p(x)\in K[x]\setminus K$. Then: $$p(x)\text{ is separable}\iff\gcd(p(x),p'(x))=1$$
  \end{corollary}
  \begin{corollary}
    Let $K$ be a field such that $\ch K=0$ and $p(x)\in K[x]$ is irreducible. Then, $p(x)$ is separable.
  \end{corollary}
  \begin{lemma}
    Let $K$ be a field such that $\ch K=p>0$ and $p(x)\in K[x]$. Then: $$p'(x)=0\iff\exists q(x)\in K[x]:p(x)=q(x^p)$$
  \end{lemma}
  \begin{corollary}
    Let $K$ be a field such that $\ch K=p>0$ and $p(x)\in K[x]$. Then, all roots of $p(x^d)$ are multiple.
  \end{corollary}
  \begin{corollary}
    Let $K$ be a field such that $\ch K=p>0$, $p(x)\in K[x]$ and $q(x):=f(x^p)+bx$, where $b\in K^*$. Then, all roots of $q(x)$ are simple.
  \end{corollary}
  \begin{theorem}
    Let $K$ be a perfect field. Then, any irreducible polynomial over $K$ is separable.
  \end{theorem}
  \subsubsection{Separable extensions}
  \begin{definition}[Separable extension]
    Let $\quot{L}{K}$ be an algebraic field extension and $\alpha\in L$. We say that $\alpha$ is \textit{separable} over $K$ is $\irr(\alpha,K)(x)$ is separable. We say that $\quot{L}{K}$ is \textit{separable} if and only if $\forall \alpha\in L$, $\alpha$ is separable over $K$.
  \end{definition}
  \begin{corollary}
    Let $K$ be a perfect field. Then, any algebraic extension $\quot{L}{K}$ is separable.
  \end{corollary}
  \begin{theorem}[Separability theorem]
    Let\\ $\quot{K(\alpha_1,\ldots,\alpha_n)}{K}$ be a finite field extension and $f:K\rightarrow L$ a field morphism such that $f(\irr(\alpha_i,K)(x))$ splits into linear factors $\forall i=1,\ldots,n$. Then, the following statements are equivalent:
    \begin{enumerate}
      \item $\quot{K(\alpha_1,\ldots,\alpha_n)}{K}$ is separable.
      \item $\alpha_1,\ldots,\alpha_n$ are separable over $K$.
      \item $|\Mor_K(K(\alpha_1,\ldots,\alpha_n),f)|=[K(\alpha_1,\ldots,\alpha_n):K]$.
    \end{enumerate}
  \end{theorem}
  \begin{prop}
    Let $F/L/K$ be a tower of fields. Then:
    \begin{enumerate}
      \item $\quot{L}{K}$ and $\quot{F}{L}$ are separable $\iff\quot{F}{K}$ is separable.
      \item If $\alpha,\beta\in L$ are algebraic over $K$, then so are $\alpha+\beta$, $\alpha\beta$ and $\alpha\beta^{-1}$ (if $\beta\ne 0$).
      \item The set $$E:=\{\alpha\in L:\alpha\text{ is separable over }K\}$$ is a subfield of $L$, the field extension $\quot{E}{K}$ is separable and if $L\ne E$, then $\forall\beta\in L\setminus E$, $\beta$ is not separable over $E$. In that case, and if the extension $\quot{L}{E}$ is algebraic, we say that $\quot{L}{E}$ is \textit{purely inseparable}.
    \end{enumerate}
  \end{prop}
  \begin{theorem}[Primitive element theorem]
    Let $\quot{L}{K}$ be a finite and separable field extension. Then, $\quot{L}{K}$ is simple.
  \end{theorem}
  \begin{definition}
    We say that a field extension $\quot{L}{K}$ is a \textit{Galois extension} (or is \textit{Galois}) if it is normal and separable.
  \end{definition}
  \begin{theorem}
    Let $\quot{L}{K}$ be a finite field extension. Then: $$\textstyle\quot{L}{K}\text{ is Galois}\iff|\Gal(\quot{L}{K})|=[L:K]$$
  \end{theorem}
  \begin{lemma}
    Let $F/L/K$ be a tower of fields such that $\quot{L}{K}$ is Galois. Then, $\quot{F}{L}$ is Galois.
  \end{lemma}
  \begin{definition}
    Let $\quot{L}{K}$ be a field extension and $(G,\cdot)$ be a group. We define the following sets:
    \begin{gather*}
      \mathcal{K}(L/K):=\{F\subseteq L:L/F/K\text{ is a tower of fields}\}\\
      \mathcal{S}(G):=\{H\subseteq G:(H,\cdot)\text{ is a subgroup of }(G,\cdot)\}
    \end{gather*}
  \end{definition}
  \begin{lemma}
    Let $H\in\mathcal{S}(\Gal(\quot{L}{K}))$ and $$L^H:=\{a\in L:\sigma(a)=a\ \forall\sigma\in H)\}$$
    Then, $L^H$ is a field (called \textit{fixed field} of $H$) and $L^H\in\mathcal{K}(\quot{L}{K})$.
  \end{lemma}
  \begin{lemma}
    Let $\quot{L}{K}$ be a field extension and $F\in \mathcal{K}(\quot{L}{K})$. Then, $\Gal(\quot{L}{F})$ is a subgroup of $\Gal(\quot{L}{K})$.
  \end{lemma}
  \begin{definition}
    Let $\quot{L}{K}$ be a field extension. We define the following functions:
    \begin{gather*}
      \function{\mathcal{F}}{\mathcal{S}(\Gal(\quot{L}{K}))}{\mathcal{K}(\quot{L}{K})}{H}{L^H}\\
      \function{\mathcal{G}}{\mathcal{K}(\quot{L}{K})}{\mathcal{S}(\Gal(\quot{L}{K}))}{F}{\Gal(\quot{L}{F})}
    \end{gather*}
  \end{definition}
  \begin{prop}
    Let $\quot{L}{K}$ be a field extension. Then:
    \begin{enumerate}
      \item $\mathcal{F}(\{\id\})=L$ and $\mathcal{F}(\Gal(\quot{L}{K}))=K$.
      \item $\mathcal{G}(L)=\{\id\}$ and $\mathcal{G}(K)=\Gal(\quot{L}{K})$.
      \item Si $H_1,H_2\in\mathcal{S}(\Gal(\quot{L}{K}))$ are such that $H_1\subseteq H_2$, then $\mathcal{F}(H_1)\supseteq \mathcal{F}(H_2)$.
      \item Si $F_1,F_2\in\mathcal{K}(\quot{L}{K})$ are such that $F_1\subseteq F_2$, then $\mathcal{G}(F_1)\supseteq \mathcal{G}(F_2)$.
      \item $H\subseteq \mathcal{G}(\mathcal{F}(H))$ $\forall H\in \mathcal{S}(\Gal(\quot{L}{K}))$.
      \item $F\subseteq \mathcal{F}(\mathcal{G}(F))$ $\forall F\in \mathcal{K}(\quot{L}{K})$.
      \item $\mathcal{F}\circ\mathcal{G}\circ\mathcal{F}=\mathcal{F}$.
      \item $\mathcal{G}\circ\mathcal{F}\circ\mathcal{G}=\mathcal{G}$.
    \end{enumerate}
  \end{prop}
\end{multicols}
\end{document}